Supplemental data to ``ARTICLE TITLE''

### 2022-09-07 additional_files/additional_file_1.tex
Add signal plots for several of the signals documented in Bandillo et al. (2017)
Add plotting of all signal and gene plots with integration into Makefile
Plot signals for all loci and all traits based on reference signals
Add vertical lines for reference signals to Manhattan plots
Generate gwas results separately from plotting scripts; integrate gene plots with the updated signal nomenclature
Plot signals on the same x-scale for all programs; only a single transcriptsGrob per plot; allow for several signals to be plotted with different colors for a given reference signal
Add reference signals

\usepackage[utf8]{inputenc} % declare encoding as utf8
\usepackage{graphicx} % to enable \includegraphics
\usepackage{flafter} % to make sure floats appear after their position in text
\usepackage{pdflscape} % allow some pages to be in landscape orientation
\usepackage{layout} % for debugging purposes, looking at page layout
\usepackage[margin=1in]{geometry} % leaves more space for text body
\usepackage[hidelinks]{hyperref} % hyperlinks from list of figures/tables
\usepackage[labelfont=bf]{caption} % format captions and make links go to figure instead of caption
\usepackage{csvsimple} % read and display csv files as tables
\usepackage{booktabs} % prettier tables
\usepackage{threeparttable} % easy addition of footnotes below tables
\usepackage{textcomp} % makes the \textdegree command available
\usepackage{tocloft} % formatting the lists of tables and figures
\usepackage{xcolor} % enable text coloring
\usepackage{calc} % makes \widthof available to set the width of the last column
\usepackage{array} % using command \arraybackslash to restore the definition of \\ after \centering
\usepackage{longtable} % allow tables to span more than one page
\usepackage{threeparttablex} % threeparttable for longtable
\usepackage{capt-of} % put caption on next page

@@

% Defining a command for manhattan plot figures
\newcommand{\manhattanplot}[1]{
\begin{cfigure}
	\caption[Figure caption]{Figure caption}
	\includegraphics[width = 6in]{#1_manhattan}
	\label{#1_manhattan}
\end{cfigure}

@@

\newcommand{\signalplot}[1]{
\begin{cfigure}
	\caption[Figure caption]{Figure caption}
	\includegraphics[width = 6in]{#1_signal}
	\label{#1_signal}
\end{cfigure}

@@

@@

% \caption[Number of SVs per Oxford Nanopore sample]{{{{

%\begin{table}
%	\caption[Number of SVs per Oxford Nanopore sample]{}
%	\label{table_s1}
%
%	\begin{threeparttable}\small
%			   \begin{tablenotes}
%			   \end{tablenotes}
%	\end{threeparttable}
%
%\end{table}
%\clearpage%}}}

% Manhattan plots of all traits
\manhattanplot{stem_termination_all}
\manhattanplot{stem_termination_sn}
\manhattanplot{pubescence_color_all}
\manhattanplot{pubescence_color_nogray}
\manhattanplot{protein}
\manhattanplot{pubescence_form_all}
\manhattanplot{pubescence_form_noerect}
\manhattanplot{oil}
\manhattanplot{pubescence_density}
\manhattanplot{seed_coat_luster_all}
\manhattanplot{seed_coat_luster_nointermediate}
\manhattanplot{seed_coat_luster_dullshiny}
\manhattanplot{pod_color_all}
\manhattanplot{pod_color_blbr}
\manhattanplot{flower_color}
\manhattanplot{seed_coat_color_all}
\manhattanplot{seed_coat_color_greenyellow}
\manhattanplot{hilum_color_all}
\manhattanplot{hilum_color_blackbrown}
\manhattanplot{hilum_color_rbr}
\manhattanplot{maturity_group}
\manhattanplot{corrected_dry_weight}

\signalplot{pca_t}
\signalplot{fc_w}
\signalplot{sda_dt1}

>>>>

\usepackage[utf8]{inputenc} % declare encoding as utf8
\usepackage{graphicx} % to enable \includegraphics
\usepackage{flafter} % to make sure floats appear after their position in text
\usepackage{pdflscape} % allow some pages to be in landscape orientation
\usepackage{layout} % for debugging purposes, looking at page layout
\usepackage[margin=1in]{geometry} % leaves more space for text body
\usepackage[hidelinks]{hyperref} % hyperlinks from list of figures/tables
\usepackage[labelfont=bf]{caption} % format captions and make links go to figure instead of caption
\usepackage{csvsimple} % read and display csv files as tables
\usepackage{booktabs} % prettier tables
\usepackage{threeparttable} % easy addition of footnotes below tables
\usepackage{textcomp} % makes the \textdegree command available
\usepackage{tocloft} % formatting the lists of tables and figures
\usepackage{xcolor} % enable text coloring
\usepackage{calc} % makes \widthof available to set the width of the last column
\usepackage{array} % using command \arraybackslash to restore the definition of \\ after \centering
\usepackage{longtable} % allow tables to span more than one page
\usepackage{threeparttablex} % threeparttable for longtable
\usepackage{capt-of} % put caption on next page
\usepackage{listings}

@@

% Defining a command to generate a table of phenotypic data for a single gwas
\newcommand{\gwastableone}[1]{
\begin{table}
	\caption{Numerical coding of phenotypic data used for the GWAS analysis of #1}
	\label{#1_gwas_table}

	\centering
	\begin{threeparttable}\small

		\csvreader[head to column names,
		/csv/separator=semicolon,
		tabular = llc,
		table head = \toprule Phenotype & Frequency & GWAS \#1 \\ \midrule,
		table foot = \bottomrule]%
		{../tables/#1_gwas_table.csv}%
		{}%
		{\Value & \Frequency & \GWASa}

			   \begin{tablenotes}
			   \item[a] test
			   \end{tablenotes}
	\end{threeparttable}

\end{table}
\clearpage
}

% Defining a command to generate a table of phenotypic data for two gwas
\newcommand{\gwastabletwo}[1]{
\begin{table}
	\caption{Numerical coding of phenotypic data used for the GWAS analysis of #1}
	\label{#1_gwas_table}

	\centering
	\begin{threeparttable}\small

		\csvreader[head to column names,
		/csv/separator=semicolon,
		tabular = llcc,
		table head = \toprule Phenotype & Frequency & GWAS \#1 & GWAS \# 2\\ \midrule,
		table foot = \bottomrule]%
		{../tables/#1_gwas_table.csv}%
		{}%
		{\Value & \Frequency & \GWASa & \GWASb}

			   \begin{tablenotes}
			   \item[a] test
			   \end{tablenotes}
	\end{threeparttable}

\end{table}
\clearpage
}

% Defining a command to generate a table of phenotypic data for three gwas
\newcommand{\gwastablethree}[1]{
\begin{table}
	\caption{Numerical coding of phenotypic data used for the GWAS analysis of #1}
	\label{#1_gwas_table}

	\centering
	\begin{threeparttable}\small

		\csvreader[head to column names,
		/csv/separator=semicolon,
		tabular = llccc,
		table head = \toprule Phenotype & Frequency & GWAS \#1 & GWAS \# 2 & GWAS \# 3\\ \midrule,
		table foot = \bottomrule]%
		{../tables/#1_gwas_table.csv}%
		{}%
		{\Value & \Frequency & \GWASa & \GWASb & \GWASc}

			   \begin{tablenotes}
			   \item[a] test
			   \end{tablenotes}
	\end{threeparttable}

\end{table}
\clearpage
}

% Defining a command for manhattan plot figures
\newcommand{\manhattanplot}[1]{
\begin{cfigure}
	\includegraphics[width = 6in]{#1_manhattan}
	\caption{#1\_manhattan}
	\label{#1_manhattan}
\end{cfigure}

@@

\newcommand{\signalplot}[1]{
\begin{cfigure}
	\includegraphics[width = 6in]{#1_signal}
	\caption{#1\_signal}
	\label{#1_signal}
\end{cfigure}

@@

\newcommand{\geneplot}[1]{
\begin{cfigure}
	\includegraphics[width = 6in]{#1_gene}
	\caption{#1\_gene}
	\label{#1_gene}
\end{cfigure}

% Allows underscores in captions but is not a great solution
\catcode`_=12

@@

\gwastableone{FLOWER.COLOR}
\gwastabletwo{PUBESCENCE.COLOR}
\gwastabletwo{SEED.COAT.COLOR}
\gwastabletwo{STEM.TERMINATION.TYPE}
\gwastablethree{HILUM.COLOR}
\gwastabletwo{POD.COLOR}
\gwastabletwo{PUBESCENCE.FORM}
\gwastableone{PUBESCENCE.DENSITY}
\gwastablethree{SEED.COAT.LUSTER}
\gwastableone{MATURITY.GROUP}

\manhattanplot{flower_color}
\signalplot{flower_color_W1}
\geneplot{flower_color_W1}
%\signalplot{flower_color_L1}
%\geneplot{flower_color_L1}

\manhattanplot{pubescence_color_all}
%\signalplot{pubescence_color_all_Td}
\signalplot{pubescence_color_all_T}
\geneplot{pubescence_color_all_T}

\manhattanplot{pubescence_color_nogray}
\signalplot{pubescence_color_nogray_Td}
%\signalplot{pubescence_color_nogray_T}
%\geneplot{pubescence_color_nogray_T}

\manhattanplot{seed_coat_color_all}
\signalplot{seed_coat_color_all_G}
\signalplot{seed_coat_color_all_T}
\geneplot{seed_coat_color_all_T}
\signalplot{seed_coat_color_all_O}
\signalplot{seed_coat_color_all_I}
\geneplot{seed_coat_color_all_I}
%\signalplot{seed_coat_color_all_R}
%\geneplot{seed_coat_color_all_R}

\manhattanplot{seed_coat_color_greenyellow}
\signalplot{seed_coat_color_greenyellow_G}
%\signalplot{seed_coat_color_greenyellow_T}
%\geneplot{seed_coat_color_greenyellow_T}
%\signalplot{seed_coat_color_greenyellow_O}
%\signalplot{seed_coat_color_greenyellow_I}
%\geneplot{seed_coat_color_greenyellow_I}
%\signalplot{seed_coat_color_greenyellow_R}
%\geneplot{seed_coat_color_greenyellow_R}

\manhattanplot{stem_termination_all}
%\signalplot{stem_termination_all_Dt2}
%\geneplot{stem_termination_all_Dt2}
\signalplot{stem_termination_all_Dt1}
\geneplot{stem_termination_all_Dt1}
%\signalplot{stem_termination_all_E3}
%\geneplot{stem_termination_all_E3}

\manhattanplot{stem_termination_sn}
%\signalplot{stem_termination_sn_Dt2}
%\geneplot{stem_termination_sn_Dt2}
\signalplot{stem_termination_sn_Dt1}
\geneplot{stem_termination_sn_Dt1}
%\signalplot{stem_termination_sn_E3}
%\geneplot{stem_termination_sn_E3}

\manhattanplot{hilum_color_all}
\signalplot{hilum_color_all_T}
\geneplot{hilum_color_all_T}
%\signalplot{hilum_color_all_O}
\signalplot{hilum_color_all_I}
\geneplot{hilum_color_all_I}
\signalplot{hilum_color_all_R}
\geneplot{hilum_color_all_R}
%\signalplot{hilum_color_all_W1}
%\geneplot{hilum_color_all_W1}

\manhattanplot{hilum_color_blackbrown}
%\signalplot{hilum_color_blackbrown_T}
%\geneplot{hilum_color_blackbrown_T}
%\signalplot{hilum_color_blackbrown_O}
%\signalplot{hilum_color_blackbrown_I}
%\geneplot{hilum_color_blackbrown_I}
\signalplot{hilum_color_blackbrown_R}
\geneplot{hilum_color_blackbrown_R}
%\signalplot{hilum_color_blackbrown_W1}
%\geneplot{hilum_color_blackbrown_W1}

\manhattanplot{hilum_color_rbr}
%\signalplot{hilum_color_rbr_T}
%\geneplot{hilum_color_rbr_T}
%\signalplot{hilum_color_rbr_O}
%\signalplot{hilum_color_rbr_I}
%\geneplot{hilum_color_rbr_I}
%\signalplot{hilum_color_rbr_R}
%\geneplot{hilum_color_rbr_R}
%\signalplot{hilum_color_rbr_W1}
%\geneplot{hilum_color_rbr_W1}

\manhattanplot{pod_color_all}
\signalplot{pod_color_all_L2}
\signalplot{pod_color_all_L1}
\geneplot{pod_color_all_L1}

\manhattanplot{pod_color_blbr}
%\signalplot{pod_color_blbr_L2}
\signalplot{pod_color_blbr_L1}
\geneplot{pod_color_blbr_L1}

\manhattanplot{pubescence_form_all}
\signalplot{pubescence_form_all_Pa1}
\signalplot{pubescence_form_all_Pa2}

\manhattanplot{pubescence_form_noerect}
\signalplot{pubescence_form_noerect_Pa1}
%\signalplot{pubescence_form_noerect_Pa2}

\manhattanplot{pubescence_density}
%\signalplot{pubescence_density_Pd1}
\signalplot{pubescence_density_Ps}
%\signalplot{pubescence_density_P1}
%\geneplot{pubescence_density_P1}

\manhattanplot{seed_coat_luster_all}
%\signalplot{seed_coat_luster_all_I}
%\geneplot{seed_coat_luster_all_I}
%\signalplot{seed_coat_luster_all_Bq}
%\signalplot{seed_coat_luster_all_B1}
\signalplot{seed_coat_luster_all_Hps}
\geneplot{seed_coat_luster_all_Hps}
\signalplot{seed_coat_luster_all_B}

\manhattanplot{seed_coat_luster_nointermediate}
%\signalplot{seed_coat_luster_nointermediate_I}
%\geneplot{seed_coat_luster_nointermediate_I}
%\signalplot{seed_coat_luster_nointermediate_Bq}
%\signalplot{seed_coat_luster_nointermediate_B1}
\signalplot{seed_coat_luster_nointermediate_Hps}
\geneplot{seed_coat_luster_nointermediate_Hps}
\signalplot{seed_coat_luster_nointermediate_B}

\manhattanplot{seed_coat_luster_dullshiny}
%\signalplot{seed_coat_luster_dullshiny_I}
%\geneplot{seed_coat_luster_dullshiny_I}
%\signalplot{seed_coat_luster_dullshiny_Bq}
%\signalplot{seed_coat_luster_dullshiny_B1}
\signalplot{seed_coat_luster_dullshiny_Hps}
\geneplot{seed_coat_luster_dullshiny_Hps}
\signalplot{seed_coat_luster_dullshiny_B}

\manhattanplot{corrected_dry_weight}
\signalplot{corrected_dry_weight_cdwGm17}

\manhattanplot{maturity_group}
%\signalplot{maturity_group_E1}
%\geneplot{maturity_group_E1}
%\signalplot{maturity_group_E2}
%\geneplot{maturity_group_E2}
%\signalplot{maturity_group_E3}
%\geneplot{maturity_group_E3}
%\signalplot{maturity_group_E4}
%\geneplot{maturity_group_E4}

\manhattanplot{oil}
\signalplot{oil_oilGm15}
%\signalplot{oil_oilGm20}

\manhattanplot{protein}
%\signalplot{protein_proteinGm15}
%\signalplot{protein_proteinGm20}
